Variance reduction for Markov chains via martingale representations

### 2020-04-13 aap/Revision/vr-mcmc-revision-new-new.tex
update

A_{N+n-1,k}(X_{l-1}^{x}) \phi_{k}(\xi_{l}),

@@

For an estimator $\rho(f)\in\{\pi_n^N(f),\pi_{K,n}^N(f)\}$

@@

\mathrm{MSE}\left[\rho(f)\right] = \PE\left[\left\{\rho(f)-\pi(f)\right\}^2\right]
=\left\{\PE[\rho(f)]-\pi(f)\right\}^2 +\PVar[\rho(f)].

@@

$\pi_n^N(f)$ and $\pi_{K,n}^N(f)$ have the same  bias. Under assumptions {\bf (H1)} and {\bf (H2)}, the corresponding Markov chain has a unique stationary distribution $\pi_\gamma$, which is different from $\pi$. From \cite[Theorem~10]{durmus:moulines:2017}

@@

it follows that

@@

for some constant $C>0.$ Let us now derive an upper bound for the variance of the classical estimator~\eqref{eq:29032018a2} for ULA-based chain.

\begin{lem}
\label{lem:variance}
Let $f$ be a bounded Borel function and $(X^x_{p})_{p \in \nset_0}$ be a Markov chain generated by ULA with constant step size $\gamma$, satisfying {\bf (H1)} and {\bf (H2)}. Assume also that $n\gamma > c_0$ for some fixed $c_0>0,$ then it holds

@@

with $V(x) = 1+ \|x\|^2$ where $\lesssim$ stands for inequality up to a constant not depending on $\gamma$ and $n$.

@@

 Set $V(x) = 1 + \|x\|^2,$ then  it holds for $q=0,\ldots,n-1,$ and all $x$

>>>>

A_{N+n-l,k}(X_{l-1}^{x}) \phi_{k}(\xi_{l}),

@@

For an estimator $\rho_n^N(f)\in\{\pi_n^N(f),\pi_{K,n}^N(f)\}$

@@

\mathrm{MSE}\left[\rho_n^N(f)\right] = \PE\left[\left\{\rho_n^N(f)-\pi(f)\right\}^2\right]
=\left\{\PE[\rho_n^N(f)]-\pi(f)\right\}^2 +\PVar[\rho_n^N(f)].

@@

$\pi_n^N(f)$ and $\pi_{K,n}^N(f)$ have the same  bias. Under assumptions {\bf (H1)} and {\bf (H2)}, the corresponding Markov chain has a unique stationary distribution $\pi_\gamma$, which is different from $\pi$. From \cite[Theorem~10]{durmus:moulines:2017},

@@

it follows that there exist $\gamma_0 > 0$ and $C < \infty$ such that for all $\gamma \in (0,\gamma_0]$, we get

@@

 Let us now derive an upper bound for the variance of the classical estimator~\eqref{eq:29032018a2} for ULA-based chain. Define
 \label{eq:definition-V}
 V(x) = 1+ \|x\|^2 \,.
\begin{lem}
\label{lem:variance}
Let $f$ be a bounded Borel function and $(X^x_{p})_{p \in \nset_0}$ be a Markov chain generated by ULA with constant step size $\gamma \in (0,\gamma_0]$ where $\gamma_0= m/L^2$. 
Let $c_0>0$. Then, for all $n \in \nset$, $\gamma \in (0,\gamma_0]$ satisfying $n\gamma > c_0$   

@@

where $\lesssim$ stands for inequality up to a constant not depending on $\gamma \in (0,\gamma_0]$ and $n \in \nset$.

@@

Then, it holds that for $q=0,\ldots,n-1,$ and all $x$
